\clearpage
\newpage
\chapter{Summary}

\section{Summary of the $\wpr$ Search}
We have performed a search for new physics in the boosted $\tbbar$ all
hadronic final state.  The main feature of this topology is a top quark
whose decay products merge into a single jet. 

We take advantage of additional information provided by the top jet
substructure to increase the sensitivity of the analysis.  The main background for
the search is QCD multijet production, and is predicted by using the
average rate of b-tagging derived from the jet substructure sideband
region.  The other main source of background (SM $\ttbar$ production) is taken from 
the Monte Carlo simulation and corrected by a data-driven scale factor.

Using 19.7$~\fbinv$ of integrated luminosity collected in 2012 by the
LHC, we exclude a right-handed $\wpr$ particle with invariant mass
below 2.02 $\TeV$.  Additionally, we exclude the left-handed and mixed-coupling $\wpr$ particles at 1.94 $\TeV$ and 2.14 $\TeV$ respectively.

The combined semileptonic and fully-hadronic channels increase the sensitivity of the cross-section limit.  
Using the conbined sensitivity of the two channels, we exclude a right-handed $\wpr$ particle with invariant mass below 2.15$~\TeV$  



\section{Summary of the $\bs$ Search}
We have performed a search for new physics in the boosted tW all
hadronic final state.  The main feature of a typical event is a boosted top quark and W boson
whose decay products merge into single jets resulting in a dijet topology. 

We take advantage of additional information provided by the 
substructure of these merged jets  to increase the sensitivity of the analysis.  The main background for
the search is QCD multijet production, and is predicted by using the
average top-mistagging rate derived from the jet substructure sideband
region.  The other main source of background (SM $\ttbar$ production) is taken from 
the Monte Carlo simulation and corrected by a data-driven scale factor.

Using 19.7$~\fbinv$ of integrated luminosity collected in 2012 by the
LHC, the production of a right-handed b* with mass between 0.82 TeV and 1.43 TeV, 
left-handed b* with mass between 0.88 TeV and 1.39 TeV, 
and vectorlike b* with mass between 0.8 TeV and 1.53 TeV is excluded at the 95\% confidence level.

The combined semileptonic, dileptonic, and fully-hadronic channels increase the sensitivity of the cross-section limit.  
Using the conbined sensitivity of the two channels, we exclude a right-handed $\bs$ particle with invariant mass below 1.42$~\TeV$, 
a left-handed $\bs$ with invariant mass below 1.39$~\TeV$, and a vectorlike $\bs$ with invariant mass below 1.52$~\TeV$.

