
\chapter{The $\wpr$ Search}
\section{Introduction}
\label{sec:introduction}

Many beyond the BSM theories predict new massive
gauge bosons.  This note presents a search for a heavy partner of
the SM W gauge boson, generally referred to as the
$\wpr$ (see Chapter~\ref{sec:BSMtheory}).  
We focus on the $\wpr \to \tbbar$ decay mode motivated by the ability to lower QCD multijet background in this channel when compared to light flavor hadronic decay modes. 


The primary signal under investigation is a $\wpr$ particle in which the interaction with quarks 
is defined by the following Lagrangian,
\begin{eqnarray}
{\cal L} = \frac{V_{q_iq_j}}{2\sqrt{2}} g_w \overline{q}_i\gamma_\mu 
\bigl( a^R_{q_iq_j} (1+{\gamma}^5) + a^L_{q_iq_j}
(1-{\gamma}^5)\bigr) {\wpr} q_j + \mathrm{H.c.} \,,
\label{eqn:Lag}
\end{eqnarray}
This is the most general, lowest-dimensional, model-independent
effective Lagrangian for the $\wpr$ boson.  Here $a_{qi,qj}^{L}$,
$a_{qi,qj}^{R}$ are the left- and right-handed couplings of $\wpr$ to quarks.
For a SM-like $\wpr$, $a_{qi,qj}^{L}$=1, $a_{qi,qj}^{R}=0$.


Searches for a high mass $\wpr$ resonance have been performed at the
Tevatron \cite{PhysRevLett.100.211803,Abazov2011145} and at CMS \cite{CMS-PAS-B2G-12-010,CMS-PAS-EXO-12-060,CMS-PAS-EXO-12-025} and ATLAS \cite{PhysRevLett.109.081801} at the LHC.  
Currently, the most stringent limits on $\wpr$ cross-sections exclude a right-handed $\wpr$ particle with mass below 2.05$~\TeV$ at the 95\% C.L. In this analysis we do not consider \wpr\
  lighter than $\sim$~1.3~$\TeV$ since there are stringent limits on $\wpr$ production at these masses.  

We present a search for $\wpr \to \tbbar$ followed by the
fully hadronic decay chain $\mathrm{t \to W+b}$ followed by $\mathrm{W \to hadrons}$.
This differs from \cite{CMS-PAS-B2G-12-010} since the final state is
comprised of only jets.  In our kinematic regime of interest ($\mathrm{M_{\wpr}
\gtrsim 1.3~\TeV}$) the top quark is quite energetic, and due to its Lorentz
boost, the angular separation between its immediate decay products will
be small.  The jets resulting from the hadronization of the b quark
and the light quarks from W boson from the top decay usually overlap, resulting in one
`fat' jet.  This search uses special techniques to identify the
substructure of this top jet, and further selection based on
substructure information as well as b-tagging strongly suppresses the
QCD background.

The search uses $19.7~\fbinv$ of 8$~\TeV$ data collected from
the CMS experiment in 2012.
